---
output: github_document
editor_options: 
  chunk_output_type: inline
---

<!-- File.md is generated from File.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
library(knitr)
```


# CCAMLRGIS R package

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/CCAMLRGIS)](https://cran.r-project.org/package=CCAMLRGIS)
[![R-hub](https://github.com/ccamlr/CCAMLRGIS/actions/workflows/rhub.yaml/badge.svg)](https://github.com/ccamlr/CCAMLRGIS/actions/workflows/rhub.yaml)
[![All downloads](https://cranlogs.r-pkg.org/badges/grand-total/CCAMLRGIS)](https://cran.r-project.org/package=CCAMLRGIS)
[![Monthly downloads](https://cranlogs.r-pkg.org/badges/CCAMLRGIS)](https://cran.r-project.org/package=CCAMLRGIS)
<!-- badges: end -->

This package was developed to simplify the production of maps in the CAMLR Convention Area. It provides two main categories of functions: load functions and create functions. Load functions are used to import spatial layers from the online [CCAMLR GIS](https://gis.ccamlr.org/) such as the ASD boundaries. Create functions are used to create layers from user data such as polygons and grids.

## Installation

You can install the CCAMLRGIS R package from CRAN with:

```{r, eval = F}
install.packages("CCAMLRGIS")
```

## Documentation

```{r, echo = FALSE, message = FALSE}
set.seed(1234)
```

<center>
### A package to load and create spatial data, including layers and tools that are relevant to CCAMLR activities.
</center>

------------------------------------------------------------------------

<center>
### Table of contents
</center>

------------------------------------------------------------------------

1.  [Basemaps](#1-basemaps)
2.  [Create functions](#2-create-functions)
